Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-11-21 ms/ms.Rmd
ms: minor edit

Soil science needs more studies of relationships between peat depth and topographic or radiometric data to determine which variables are most predictive, how predictive they are, and how consistent their associations.
The push for nature-based climate solutions motivates for broad mapping of peat depth, to identify rich peatland carbon stocks and avoid their conversion.
Although small areas can be mapped accurately on the ground, having landscape-scale maps *before* detailed investigation increases the option space for spatial planning and land management. 
For example, the Norwegian Public Roads Administration routinely measures peat depth during geotechnical work, but by that time, the route of the road is already set. 
With a digital peat depth map, planners could better compare routes and climate mitigation measures would have more leverage.

>>>>

Soil science needs more studies of relationships between peat depth and topographic or radiometric data to determine how predictive they are, which variables are most predictive, and how consistent their associations.
The push for nature-based climate solutions motivates for broad mapping of peat depth, to identify rich peatland carbon stocks and avoid their conversion.
Although small areas can be mapped accurately on the ground, having landscape-scale maps *before* detailed investigation increases the option space for spatial planning and land management. 
For example, the Norwegian Public Roads Administration routinely measures peat depth during geotechnical work, but by that time, the route of the road is already set. 
With a digital peat depth map, planners could better compare routes and climate mitigation measures would have more leverage.

### 2024-11-21 ms/ms.tex
ms: minor edit

Soil science needs more studies of relationships between peat depth and topographic or radiometric data to determine which variables are most predictive, how predictive they are, and how consistent their associations.
The push for nature-based climate solutions motivates for broad mapping of peat depth, to identify rich peatland carbon stocks and avoid their conversion.
Although small areas can be mapped accurately on the ground, having landscape-scale maps \emph{before} detailed investigation increases the option space for spatial planning and land management.
For example, the Norwegian Public Roads Administration routinely measures peat depth during geotechnical work, but by that time, the route of the road is already set.
With a digital peat depth map, planners could better compare routes and climate mitigation measures would have more leverage.

>>>>

Soil science needs more studies of relationships between peat depth and topographic or radiometric data to determine how predictive they are, which variables are most predictive, and how consistent their associations.
The push for nature-based climate solutions motivates for broad mapping of peat depth, to identify rich peatland carbon stocks and avoid their conversion.
Although small areas can be mapped accurately on the ground, having landscape-scale maps \emph{before} detailed investigation increases the option space for spatial planning and land management.
For example, the Norwegian Public Roads Administration routinely measures peat depth during geotechnical work, but by that time, the route of the road is already set.
With a digital peat depth map, planners could better compare routes and climate mitigation measures would have more leverage.
